---
title: "Symbolic Material Culture within an Ancient Catastrophic Temple Complex"
author: Dr. Henry Walton Jones Jr.
date: "1984"
format: html
engine: knitr
execute: 
  echo: false
  warning: false
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(here)
mortuary_data <- read_csv(here("data/mortuary_clean.csv"))
```


## Introduction

This is a **totally** made up study. The 
*data* are ***VERY*** real though.  
It is very important to state that any 
conclusions reached in this article are
the ramblings of a fictional
archaeologist.

New paragraph.

## Materials

Here is a list of materials used during excavation:

- Whip
  + for careful excavation
- Hat
  + protection from sun
- Gun
  * to keep away dig-site cats
  
1. Gun
2. Whip
3. Hat

## Methods

I recently learned R, which is why I'm using it here. I'm using `r version$version.string`.


## Results

| Column 1 | Column 2 | Column 3 |
|----|----|------------|
| Item | Another item | A third item |

```{r}
mortuary_data |>
  mutate(Area = Length * Width) |>
  group_by(Phase) |>
  summarise(
    mean = mean(Area, na.rm = T),
    sd = sd(Area, na.rm = T)
  ) |>
  arrange(desc(mean)) |>
  knitr::kable()
```

Let's make a figure.

```{r}
mortuary_data |>
  filter(Phase != "disturbed") |>
  mutate(Area = Length * Width) |>
  ggplot(aes(x = Phase, y = Area)) +
  geom_violin() +
  geom_boxplot() 
```




